Hydras \& Co.

### 2022-03-03 doc/gaia-chapter.tex
add references to gaia in chapter 4

\subsubsection{Pretty printing Cantor normal forms}

@@

\subsubsection{Order and comparison}
Leibniz equality and strict order on both libraries are
compatible:

@@

\subsubsection{Cantor normal form}

Both definitions of ``being in Cantor normal form'' are
compatible.

>>>>

\subsubsection{Pretty printing Cantor normal forms}
\label{sect:gaia-ppT1}

@@

\subsubsection{Order and comparison}
\label{sect:lt-compat-gaia}
Leibniz equality and strict order on both libraries are
compatible:

@@

\subsubsection{Cantor normal form}
\label{nf-gaia-compat}
Both definitions of ``being in Cantor normal form'' are
compatible.

### 2022-03-03 doc/part-hydras.tex
minor corrections
add references to gaia in chapter 4

\begin{gaiacompat}

@@

\end{gaiacompat}

@@

@@

@@

@@

@@

>>>>

\paragraph{\gaiacompat}

@@

@@

\paragraph{\gaiacompat}
In \texttt{gaia.ssete9}, the ordinal $\omega$ is bound to
a \emph{constant} called \texttt{T1omega}.

@@

\paragraph{\gaiacompat}
In \texttt{gaia.ssete9} the identifier\texttt{phi0} is bound to a constant (not a notation).

@@

\paragraph{\gaiacompat}
In ~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge},
we define a variant of \texttt{pp} for pretty-printing terms of type \texttt{ssete9.CantorOrdinal.T1} (see Sect.~\vref{sect:gaia-ppT1}).

@@

\paragraph{\gaiacompat}
In \gaia, the strict order \texttt{T1lt} on ordinal terms is directly defined as a boolean function (in \ssreflect's style).

\inputsnippets{nfwfgaia/T1ltDef}

In section~\vref{sect:lt-compat-gaia}, we show that both definitions are mutually equivalent.

@@

\paragraph{\gaiacompat}
In \gaia, the boolean function which characterizes ordinal terms in normal form is defined as follows:

\inputsnippets{nfwfgaia/T1nfDef}

In Sect.~\vref{nf-gaia-compat}, we show that \gaia's \texttt{T1nf} is extensionnaly equivalent with \HydrasLib'  \texttt{nf}.
